Selecting the Maximum-Utility Web Services Using Circuits

### 2009-12-13 publicaciones/eswc10/paperESWC10.tex
pequeñas correcciones a paper de mvidal

\institute{Universidad Sim\'on Bol\'{\i}var\\
                Caracas, Venezuela\\
                \{idaniel,bonet,mvidal\}ldc.usb.ve} \maketitle
\begin{abstract}
In Service Oriented Architectures (SOA), concrete services are described in terms of functionality   and QoS parameters, while software applications are specified as workflows of abstract services and non-functional criteria that establish the  application desirable functionality and  expected quality, respectively.  During workflow execution time,  abstract services  are rewritten 
with the concrete services  that meet the workflow  functional and non-functional restrictions. Since, service selection is done on-the-flight and the space of concrete services may be very large, efficiency and scalability are required.  In this paper we propose the {\it McdSat}$^c$ framework to efficiently solve the problem of service selection in presence of a large number of concrete services.
First, we use the Local As View approach to describe the functionality  of the concrete services in terms of views of abstract services, the quality as an overall utility function that combines the different QoS values that describe the service, and  workflows as  conjunctive queries on abstract services. Based on this representation, we 
model the problem of service selection as a known problem in the area of integration systems referred as query rewriting using views.  We encode the service selection problem as a propositional theory whose models correspond to the composition of the services that implement the abstract workflow and maximizes the overall utility function; known relationships between d-DNNF theories and arithmetic circuits are exploited to provide an efficient and scalable solution.  We report on the performance of our proposed approach, and we observe that  {\it McdSat}$^c$  efficiently scales up to large instances of the service selection problem.

@@

In order to design an application, users usually specify the functionality in terms of a workflow of abstract services, while the desirable quality  is defined by restricting the values of the QoS parameters that describe the concrete available services. To evaluate the proposed workflow,  abstract services are instantiated on concrete services in a way restrictions on the QoS parameters are satisfied.  However, the performance of this tasks is impacted by the number of available sources,  techniques enable to efficiently scale up to a large number of services are required.

@@

In {\it MCDSat}$^c$, concrete service functionalities are decribed as views on abstract services and workflows are represented as conjunctive queries on abstract services; this service representation is similar to the one generated in a semi-automatic way for the {\cal DEIMOS} system ~\cite{AmbiteISWC09}.  In addition, rules that define workflows and  concrete services in the {\it MCDSat}$^c$ catalog,  are created in a way that input and output restrictions of the combined abstract services are satisfied. To represent the QoS measures, each concrete service description is annotated with a real number that represents an overall value of the QoS measures of this service.  Finally, {\it MCDSat}$^c$ models the web service selection problem as the problem of query rewriting using views \cite{halevy:survey}. This problem is important in the context of data integration
\cite{Chen05,JaudoinPRST05}, and query optimization and data maintenance \cite{AfratiLU07,levy:bucket}, and several approaches have been defined to efficiently scale up to a large number of views~\cite{arvelo:aaai06,pods:DuschkaG97,sac:DuschkaG97,levy:bucket,pottinger:minicon}. In this paper we propose the {\it MCDSat}$^c$ framework which extends the approach proposed in ~\cite{arvelo:aaai06},  with the capability of dealing with constants and identifying the composition of services that maximizes a given utility function.

@@

The composition {\it wi2} is not valid because  it maps the workflow variable
{\it y2} into constants {\it "CCS"} and {\it "WAS"} which denote different cities.
On the other hand, the composition {\it wi3} does not implement the workflow because the concrete service  {\it onestop} does not receive as input or produce as output, the city where the flight stops (represented by the variable {\it y1}); thus, it is not possible to ensure that the city where this flight stops and the end city  retrieved by the service {\it national}, are the same.

To avoid producing not valid workflow implementations, it is required to handling constants in a way that different constants are not mapped into
each other either directly or indirectly (via transitivity). In addition,  all the attributes in the workflow output  or needed to join other services in the workflow, have to be produced by the selected concrete service.

In addition, suppose each concrete service is annotated with a utility function that aggregates the values of different QoS that characterize the behavior of the service. Then, since the space of valid service compositions of an abstract workflow can be very large, it is required a technique able to identify the ones that maximize the utility function  without having to enumerate the whole set of valid compositions. In this paper, we propose a Propositional logic-based  approach that takes advantage of the  power of  modern SAT solvers, to efficiently enumerate the service compositions that correspond to valid implementations of a given abstract workflow, as well as the compositions that maximize a given utility function.

@@

\begin{description}
\item[Service Selection Solutions] \mbox{}\\
The problem of selecting the services that implement an abstract workflow and best meet the QoS-based criteria  is known as the QoS-aware service selection or composition problem, which has been shown to be NP-hard~\cite{Hiroshi2008}. This problem is a combinatorial optimization problem and several heuristics have been proposed to find a relatively good solution in a reasonably short period of time.  A  distance metric-based heuristic  to drive a backward search algorithm  is proposed~\cite{rahmani08}; this metric induces an order of the services in a way that sink nodes are unlikely to be visited. In ~\cite{berardi05,berardi08,berardi06}, services and workflows are described in terms of deterministic finite state machines that are encoded as a Description Logic theory whose models correspond to solutions of the problem;  although reasoning methods for Description Logics formalisms could be exploited, scalability or performance of the proposed solution has not been reported.  ~\cite{myoung08} propose a constraint-based approach that encodes the non-functional permissible values as a set of constraints whose violation needs to be minimized; to traverse the space of possibly optimal solutions, a hybrid algorithm that combines the tabu search and simulating annealing meta-heuristics is implemented; experimental results show that the proposed solution is able to scale up to a large number of services and abstract processes.  In ~\cite{cardellini07} the QoS-aware service composition problem is encoded as a Linear Programming problem providing a scalable solution to the problem.  In ~\cite{Hiroshi2008}  this problem  is defined as a multi-objective optimization problem where the different QoS parameters are considered equally important and there is not an aggregated function to combine all of them; a genetic-based algorithm is proposed to identify a set of non-dominated service compositions that best meet all the QoS parameters.  ~\cite{alrifaiR09} propose a two-fold solution that uses a hybrid integer programming algorithm to find the decomposition of global QoS into local constraint, and then,  selects the services that best meet the local constraints.   
Recently,  two new planning-based approaches have been proposed~\cite{kuterG09,sohrabiM09}.  ~\cite{kuterG09} extend the SHOP2 planning algorithm to select the trustworthy composition of services that implement a given OWL-S process model, while ~\cite{sohrabiM09}  propose a HTN planning-based solution where user preference metrics and domain regulations are used to guide the planner into the space of relevant compositions. Finally, ~\cite{lecue09} proposes a genetic-based algorithm to identify the composition of services that best meet the quality criteria for a set of QoS parameters.

@@

\begin{description}
\item[Dataset and Query Benchmark:]  we conducted our experiments over a benchmark that includes XX queries and a set of  YY views. Queries and views are starts and chains, and they have between ZZ and fTT constants; queries have QQ sub-subgoals.
\item[Evaluation Metrics:] we report on runtime performance which corresponds to the  {\it user time} produced by the {\it time} command of the Unix operation system. 
\end{description}

>>>>

\institute{Universidad Sim\'on Bol\'{\i}var\\
                Caracas, Venezuela\\
                \{idaniel,bonet,mvidal\}ldc.usb.ve} \maketitle
\begin{abstract}
In Service Oriented Architectures (SOA), concrete services are described in terms of functionality   and QoS parameters, while software applications are specified as workflows of abstract services and non-functional criteria that establish the  application desirable functionality and  expected quality, respectively.  During workflow execution time,  abstract services  are rewritten 
with the concrete services  that meet the workflow  functional and non-functional restrictions. Since, service selection is done on-the-flight and the space of concrete services may be very large, efficiency and scalability are required.  In this paper we propose the {\it McdSat}$^c$ framework to efficiently solve the problem of service selection in presence of a large number of concrete services.
First, we use the Local As View approach to describe the functionality  of the concrete services in terms of views of abstract services, the quality as an overall utility function that combines the different QoS values that describe the service, and  workflows as  conjunctive queries on abstract services. Based on this representation, we 
model the problem of service selection as a known problem in the area of integration systems referred as query rewriting using views.  We encode the service selection problem as a propositional theory whose models correspond to the composition of the services that implement the abstract workflow and have the same cost as the corresponding composition; known relationships between d-DNNF theories and arithmetic circuits are exploited to provide an efficient and scalable solution.  We report on the performance of our proposed approach, and we observe that  {\it McdSat}$^c$  efficiently scales up to large instances of the service selection problem.

@@

In order to design an application, users usually specify the functionality in terms of a workflow of abstract services, while the desirable quality  is defined by restricting the values of the QoS parameters that describe the concrete available services. To evaluate the proposed workflow,  abstract services are instantiated on concrete services in a way restrictions on the QoS parameters are satisfied.  However, since the number of available sources has an impact on the performance of this task, techniques that enable us to efficiently scale up to a large number of services are required.

@@

In {\it MCDSat}$^c$, concrete service functionalities are described as views on abstract services and workflows are represented as conjunctive queries on abstract services; this service representation is similar to the one generated in a semi-automatic way for the {\cal DEIMOS} system ~\cite{AmbiteISWC09}.  In addition, rules that define workflows and  concrete services in the {\it MCDSat}$^c$ catalog,  are created in a way that input and output restrictions of the combined abstract services are satisfied. To represent the QoS measures, each concrete service description is annotated with a real number that represents an overall value of the QoS measures of this service.  Finally, {\it MCDSat}$^c$ models the web service selection problem as the problem of query rewriting using views \cite{halevy:survey}. This problem is important in the context of data integration
\cite{Chen05,JaudoinPRST05}, and query optimization and data maintenance \cite{AfratiLU07,levy:bucket}, and several approaches have been defined to efficiently scale up to a large number of views~\cite{arvelo:aaai06,pods:DuschkaG97,sac:DuschkaG97,levy:bucket,pottinger:minicon}. In this paper we propose the {\it MCDSat}$^c$ framework which extends the approach proposed in ~\cite{arvelo:aaai06},  with the capability of dealing with constants and identifying the composition of services that maximizes a given utility function.

@@

The composition {\it wi2} is not valid because  it maps the workflow variable
{\it y2} into constants {\it "CCS"} and {\it "WAS"} which denote different cities.
On the other hand, the composition {\it wi3} does not implement the workflow because the concrete service  {\it onestop} does not receive as input or produce as output the city where the flight stops (represented by the variable {\it y1}); thus, it is not possible to ensure that the city where this flight stops and the end city  retrieved by the service {\it national}, are the same.

To avoid producing invalid workflow implementations, it is required to handle constants in a way that different constants are not mapped into
each other either directly or indirectly (via transitivity). In addition,  all the attributes in the workflow output  or needed to join other services in the workflow, have to be produced by the selected concrete service.

In addition, suppose each concrete service is annotated with a utility function that aggregates the values of different QoS that characterize the behavior of the service. Then, since the space of valid service compositions of an abstract workflow can be very large, we require a technique able to identify the ones that maximize the utility function  without having to enumerate the whole set of valid compositions. In this paper, we propose a Propositional logic-based  approach that takes advantage of the  power of  modern SAT solvers, to efficiently enumerate the service compositions that correspond to valid implementations of a given abstract workflow, as well as the compositions that maximize a given utility function.

@@

\begin{description}
\item[Service Selection Solutions] \mbox{}\\
The problem of selecting the services that implement an abstract workflow and best meet the QoS-based criteria  is known as the QoS-aware service selection or composition problem, which has been shown to be NP-hard~\cite{Hiroshi2008}. This problem is a combinatorial optimization problem and several heuristics have been proposed to find a relatively good solution in a reasonably short period of time.  A  distance metric-based heuristic  to drive a backward search algorithm  is proposed~\cite{rahmani08}; this metric induces an order of the services in a way that sink nodes are unlikely to be visited. In ~\cite{berardi05,berardi08,berardi06}, services and workflows are described in terms of deterministic finite state machines that are encoded as a Description Logic theory whose models correspond to solutions of the problem;  although reasoning methods for Description Logics formalisms could be exploited, scalability or performance of the proposed solution has not been reported.  ~\cite{myoung08} propose a constraint-based approach that encodes the non-functional permissible values as a set of constraints whose violation needs to be minimized; to traverse the space of possibly optimal solutions, a hybrid algorithm that combines the tabu search and simulated annealing meta-heuristics is implemented; experimental results show that the proposed solution is able to scale up to a large number of services and abstract processes.  In ~\cite{cardellini07} the QoS-aware service composition problem is encoded as a Linear Programming problem providing a scalable solution to the problem.  In ~\cite{Hiroshi2008}  this problem  is defined as a multi-objective optimization problem where the different QoS parameters are considered equally important and there is not an aggregated function to combine all of them; a genetic-based algorithm is proposed to identify a set of non-dominated service compositions that best meet all the QoS parameters.  ~\cite{alrifaiR09} propose a two-fold solution that uses a hybrid integer programming algorithm to find the decomposition of global QoS into local constraint, and then,  selects the services that best meet the local constraints.   
Recently,  two new planning-based approaches have been proposed~\cite{kuterG09,sohrabiM09}.  ~\cite{kuterG09} extend the SHOP2 planning algorithm to select the trustworthy composition of services that implement a given OWL-S process model, while ~\cite{sohrabiM09}  propose a HTN planning-based solution where user preference metrics and domain regulations are used to guide the planner into the space of relevant compositions. Finally, ~\cite{lecue09} proposes a genetic-based algorithm to identify the composition of services that best meet the quality criteria for a set of QoS parameters.

@@

\begin{description}
\item[Dataset and Query Benchmark:]  we conducted our experiments over a benchmark that includes XX queries and a set of  YY views. Queries and views are starts and chains, and they have between ZZ and TT constants; queries have QQ sub-subgoals.
\item[Evaluation Metrics:] we report on runtime performance which corresponds to the  {\it user time} produced by the {\it time} command of the Unix operation system. 
\end{description}
